---
title: "Bayesian Hierarchical Calibration with curveRbayes"
subtitle: "From preprocessed standards to posterior concentration estimates and CDAN precision profiles"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 3
    number_sections: true
    fig_width: 7
    fig_height: 4.5
vignette: >
  %\VignetteIndexEntry{Bayesian Hierarchical Calibration with curveRbayes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  comment   = "#>",
  fig.align = "center",
  eval      = requireNamespace("curveRcore", quietly = TRUE) &&
              requireNamespace("cmdstanr",   quietly = TRUE)
)
```

```{r packages, message=FALSE, warning=FALSE}
library(curveRcore)   # preprocessing, settings, data helpers
library(curveRbayes)  # this package
library(dplyr)
library(ggplot2)
library(posterior)    # summarise_draws, as_draws_df
library(bayesplot)    # mcmc_pairs, mcmc_nuts_treedepth
library(loo)          # loo_compare
```

---

# Ecosystem orientation {#ecosystem}

The **curveR** ecosystem contains three packages that share a common
data contract defined by curveRcore.

**curveRcore** provides data structures, the preprocessing pipeline
(`preprocess_standards()`), and settings constructors
(`new_antigen_constraints()`, `new_study_params()`, `new_fit_options()`)
used identically by both fitting engines.

**curveRbayes** (this package) fits Bayesian hierarchical dose–response
models via Stan and produces posterior concentration estimates with
full uncertainty propagation.

**curveRfreq** provides frequentist (NLS/NLME) alternatives for settings
where speed or regulatory precedent is the primary concern; a head-to-head
comparison of both engines is in the
[ecosystem comparison vignette](../curveRcore/articles/ecosystem-comparison.html).

---

# Data and preprocessing {#data}

## The raw dataset {#raw-data}

`bead_assay_example` ships with curveRbayes and contains simulated
multi-plate bead-based immunoassay data for two antigens (`alpha`,
`beta`), each measured on three plates — six `curve_id` values in total.

```{r load-data}
data("bead_assay_example", package = "curveRbayes")
str(bead_assay_example, max.level = 2, give.attr = FALSE)
```

The key design principle is that **`curve_id` is the sole foreign key**
uniquely identifying one calibration curve — encoding antigen, study,
experiment, and plate together.
`curve_id_lookup` decodes it for human-readable labels, but all fitting,
filtering, and indexing uses the integer `curve_id` alone.

```{r show-lookup}
bead_assay_example$curve_id_lookup
```

The raw `$standards` data frame carries `dilution` and `mfi`.
Neither a `concentration` column nor log-transformed responses exist
yet — those are created by preprocessing.

```{r show-raw-standards}
head(bead_assay_example$standards, 4)
```

## Preprocessing with curveRcore {#preprocessing}

`preprocess_standards()` applies four steps in a fixed canonical order,
identically for both curveRbayes and curveRfreq:

1. **Concentration computation** — `(1 / dilution) × std_curve_conc`,
   written into the `concentration` column, optionally log10-transformed.
2. **Prozone correction** — compresses post-peak hook-effect deflections.
3. **Blank handling** — one of five strategies; `"ignored"` is the default.
4. **Response log-transform** — `log10(mfi)`, non-positive values floored
   adaptively before transformation.

After preprocessing, `concentration` holds **log10(AU/mL)** and `mfi`
holds **log10(MFI)** — the exact values Stan receives, as confirmed by
`build_stan_data()` which pulls `standards$concentration` and
`standards[[response_variable]]` directly.

```{r build-settings}
# CONC in bead_assay_example runs 0.001–30 AU/mL; dilution = 1/CONC,
# so std_curve_conc = 1/min(dilution) = max(CONC) = 30.
antigen_settings <- new_antigen_constraints(
  antigen        = "alpha",
  std_curve_conc = 30,
  l_asy_method   = "default",
  pcov_threshold = 20
)

study_params <- new_study_params(
  is_log_response    = TRUE,
  is_log_independent = TRUE,
  apply_prozone      = TRUE,
  blank_option       = "ignored"
)
```

```{r preprocess}
# Preprocess all six curve_ids (both antigens, all plates)
prep <- preprocess_standards(
  data                 = bead_assay_example$standards,
  antigen_settings     = antigen_settings,
  response_variable    = bead_assay_example$response_var,
  independent_variable = bead_assay_example$indep_var,
  is_log_response      = study_params$is_log_response,
  blank_data           = bead_assay_example$blanks,
  blank_option         = study_params$blank_option,
  is_log_independent   = study_params$is_log_independent,
  apply_prozone        = study_params$apply_prozone
)

standards_preprocessed <- prep$data

# After preprocessing: concentration = log10(AU/mL), mfi = log10(MFI)
head(standards_preprocessed[, c("curve_id", "dilution",
                                 "concentration", "mfi")], 4)
```

```{r plot-preprocessed,
    fig.cap="Preprocessed calibration standards for antigen alpha (curve_id 1–3). Both axes are log10-transformed — these are the exact values passed to Stan. Each curve_id is one plate; inter-plate differences in MFI level and curve shape are the variability the hierarchical model handles."}
standards_preprocessed |>
  dplyr::filter(curve_id %in% 1:3) |>
  ggplot(aes(x = concentration, y = mfi,
             colour = factor(curve_id), group = curve_id)) +
  geom_point(size = 2.5, alpha = 0.85) +
  geom_line(linewidth = 0.5, linetype = "dashed") +
  scale_colour_brewer(palette = "Set1") +
  labs(
    x      = "log\u2081\u2080(concentration)  [AU/mL]",
    y      = "log\u2081\u2080(MFI)",
    colour = "curve_id",
    title  = "Preprocessed standards — antigen alpha"
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "bottom")
```

The three curves share the same biological dose–response but differ in
their absolute MFI offset and inflection point position — precisely the
inter-plate variability a hierarchical model is designed to handle.

---

# Fitting the model: `fit_calibration_bayes()` {#fitting}

## Argument reference {#args}

`fit_calibration_bayes()` receives already-preprocessed standards and
fits all `curve_id` values simultaneously via hierarchical Stan models.

```{r arg-table, echo=FALSE}
tibble::tribble(
  ~Argument,                 ~Default,                    ~Purpose,
  "standards",               "—",
    "Data frame. Preprocessed stacked standards with curve_id, concentration, and response column — all on the fitting scale. Output of preprocess_standards()$data.",
  "samples",                 "NULL",
    "Data frame or NULL. Stacked sample data with curve_id and response column on the raw measurement scale.",
  "response_var",            "—",
    "Character. Name of the response column (e.g. 'mfi').",
  "model_names",             "c('logistic4', 'gompertz4')",
    "Character vector. Model families to fit. loglogistic4 is automatically dropped when is_log_independent = TRUE.",
  "is_log_response",         "TRUE",
    "Logical. Whether the response column is already log10-transformed.",
  "is_log_independent",      "TRUE",
    "Logical. Whether the concentration column is already log10-transformed.",
  "std_curve_conc",          "—",
    "Numeric. Undiluted standard concentration used to build the prediction grid.",
  "fixed_a",                 "NULL",
    "Numeric or NULL. If non-NULL, a soft Normal prior is placed on the population mean of log(A) centred here. NULL = data-adaptive only.",
  "cv_x_max",                "150",
    "Numeric. Hard cap for pcov / pcov_rmse (prevents infinite CV at asymptotes).",
  "pcov_threshold",          "20",
    "Numeric. Percent CV threshold for LLOQ/ULOQ determination and the dynamic-range eligibility gate.",
  "min_dynamic_range_log10", "0.5",
    "Numeric. Minimum log10 dynamic range (upper – lower asymptote) for eligibility.",
  "max_rel_se",              "5.0",
    "Numeric. Maximum posterior SD / |mean| permitted for any per-curve parameter.",
  "n_grid",                  "200L",
    "Integer. Number of concentration points in the CDAN precision grid.",
  "grid_min_conc",           "1e-4",
    "Numeric. Lower bound of the prediction grid on the raw concentration scale.",
  "grid_max_conc",           "NULL",
    "Numeric or NULL. Upper bound of the grid. NULL uses std_curve_conc.",
  "chains",                  "4L",
    "Integer. Number of independent Markov chains.",
  "warmup",                  "1000L",
    "Integer. Warm-up iterations discarded before inference.",
  "sampling",                "1000L",
    "Integer. Post-warmup sampling iterations used for inference.",
  "adapt_delta",             "0.9",
    "Numeric. Stan adapt_delta. Increase toward 0.99 if divergences appear.",
  "seed",                    "NULL",
    "Integer or NULL. RNG seed passed to Stan for reproducibility.",
  "n_draws_predict",         "500L",
    "Integer. Posterior draws for best-model CDAN grid and sample predictions.",
  "n_draws_ensemble",        "260L",
    "Integer. Posterior draws for non-best-model CDAN grids.",
  "compute_all_grids",       "FALSE",
    "Logical. Forced TRUE automatically when > 1 model is fitted (required for eligibility gating).",
  "run_loo",                 "NULL",
    "Logical or NULL. NULL = auto (TRUE when > 1 model). Run PSIS-LOO after fitting.",
  "verbose",                 "FALSE",
    "Logical. Emit progress messages."
) |>
  knitr::kable(caption = "fit_calibration_bayes() complete argument reference.")
```

## Running the fit {#run-fit}

`fit_calibration_bayes()` receives the already-preprocessed standards
data frame from Section \@ref(preprocessing).
Preprocessing is always the caller's responsibility — the function does
not accept the raw data list.

```{r fit, results="hide"}
fit <- fit_calibration_bayes(
  standards          = standards_preprocessed,
  samples            = bead_assay_example$samples,
  response_var       = bead_assay_example$response_var,   # "mfi"
  model_names        = c("logistic4", "logistic5",
                          "gompertz4", "loglogistic5"),
  is_log_response    = study_params$is_log_response,
  is_log_independent = study_params$is_log_independent,
  std_curve_conc     = antigen_settings$standard_curve_concentration,
  fixed_a            = NULL,
  n_grid             = 200L,
  grid_min_conc      = 1e-4,
  chains             = 4L,
  warmup             = 1000L,
  sampling           = 1000L,
  adapt_delta        = 0.95,
  seed               = 42,
  run_loo            = TRUE,
  verbose            = TRUE
)
```

```{r fit-unpack}
# ── Unpack convenience references from the multiplate structure ──

# Top-level: $meta (global metadata) and $plates (per-curve results)
cat("Top-level slots:", paste(names(fit), collapse = ", "), "\n")
cat("Curve IDs fitted:", paste(names(fit$plates), collapse = ", "), "\n")
cat("Best model:", fit$meta$best_model, "\n")

# Per-curve plate for single-curve demonstrations — use curve_id "1"
cr1 <- fit$plates[["1"]]

# The per-curve ensemble: one entry per fitted model family.
# Each entry: $model_name, $converged, $parameters, $fit_stats,
#              $raw_fit (full bayes_fit object), $eligibility, $grid
ensemble <- cr1$ensemble
cat("Models in ensemble:", paste(names(ensemble), collapse = ", "), "\n")

# CmdStanMCMC fit and posterior draws for logistic4, curve_id 1
cmdstan_fit_4pl <- cr1$ensemble[["logistic4"]]$raw_fit$fit
draws_4pl       <- posterior::as_draws_df(cmdstan_fit_4pl$draws())

# LOO comparison and stacking weights from the global selection metadata
loo_comparison   <- fit$meta$selection$loo_comparison
stacking_weights <- fit$meta$selection$loo_weights
if (!is.null(stacking_weights) && is.null(names(stacking_weights)))
  names(stacking_weights) <- names(ensemble)

# Compute per-model loo objects for Pareto-k diagnostics
loo_list <- lapply(ensemble, function(m) {
  if (!is.null(m$raw_fit)) compute_loo(m$raw_fit) else NULL
})

# Assemble the flat eligibility data frame across all plates and models
eligibility <- do.call(rbind, lapply(names(fit$plates), function(cid) {
  cr <- fit$plates[[cid]]
  do.call(rbind, lapply(names(cr$ensemble), function(fam) {
    elig <- cr$ensemble[[fam]]$eligibility
    if (is.null(elig) || is.null(elig$gates)) return(NULL)
    gates_df           <- elig$gates
    gates_df$model     <- fam
    gates_df$curve_id  <- as.integer(cid)
    gates_df$eligible  <- elig$eligible
    gates_df
  }))
}))
```

---

# The `calibration_result_multiplate` output structure {#output}

`fit_calibration_bayes()` returns a single S3 object of class
`calibration_result_multiplate` (defined in curveRcore).

```{r output-names}
class(fit)
names(fit)
```

The object has two top-level slots.

**`$meta`** holds global information about the run:

```{r output-meta-table, echo=FALSE}
tibble::tribble(
  ~`fit$meta slot`,        ~Type,            ~Contents,
  "method",                "character",      "'bayesian'",
  "package",               "character",      "'curveRbayes'",
  "curve_ids",             "vector",         "All curve_id values that were fitted.",
  "n_curves",              "integer",        "Number of curve_ids.",
  "response_var",          "character",      "Name of the response column.",
  "is_log_response",       "logical",        "Whether response is log10-transformed.",
  "is_log_independent",    "logical",        "Whether concentration is log10-transformed.",
  "best_model",            "character",      "Name of the selected best model after LOO + eligibility.",
  "selection",             "list",           "Full eligible-selection object: best_model_name, criterion, assessments, eligible_models, fallback, loo_comparison, loo_weights.",
  "compute_all_grids",     "logical",        "Whether CDAN grids were computed for all models.",
  "pcov_threshold",        "numeric",        "Percent CV threshold used for LLOQ/ULOQ.",
  "timestamp",             "POSIXct",        "Wall time at which the function returned."
) |>
  knitr::kable(caption = "fit$meta slot reference.")
```

**`$plates`** is a named list with one entry per `curve_id`. Each entry is
a `calibration_result` with the following slots:

```{r output-plate-table, echo=FALSE}
tibble::tribble(
  ~`fit$plates[["k"]] slot`,     ~Type,          ~Contents,
  "meta",                        "list",          "Per-curve metadata: method, curve_id, n_standards, n_samples, chains, warmup, sampling, adapt_delta, seed, n_draws_predict, n_draws_ensemble, pcov_threshold, etc.",
  "ensemble",                    "named list",    "One entry per fitted model family (see below).",
  "selection",                   "list",          "Eligible-selection result for this plate: best_model_name, criterion, assessments_by_curve, fallback.",
  "grid",                        "data frame",    "CDAN precision grid for the selected best model at this curve_id. Columns: x_fit, predicted_response, ci_lower, ci_upper, predicted_concentration, se_concentration, pcov, pcov_rmse, pcov_pass, d2y_dx2.",
  "samples",                     "data frame",    "Back-calculated test samples for this curve_id, or NULL."
) |>
  knitr::kable(caption = "fit$plates[['k']] slot reference.")
```

Each `ensemble[[model_name]]` entry contains:

```{r output-ensemble-table, echo=FALSE}
tibble::tribble(
  ~`ensemble[[m]] slot`, ~Type,          ~Contents,
  "model_name",          "character",    "Model family identifier.",
  "converged",           "logical",      "TRUE (all Bayesian fits are considered converged; check diagnostics manually).",
  "parameters",          "data frame",   "Per-curve posterior summaries: term, mean, sd, q2.5, q50, q97.5.",
  "fit_stats",           "list",         "NUTS diagnostics: n_divergent, n_max_treedepth, ebfmi.",
  "raw_fit",             "list",         "Full fit_bayes_single() output: $fit (CmdStanMCMC), $draws (draws_df), $stan_data, $model_family.",
  "eligibility",         "list",         "assess_model_eligibility() result: eligible (logical), gates (data frame), dynamic_range_log10, lloq, uloq.",
  "grid",                "data frame",   "Per-model CDAN grid at this curve_id (populated for all models when compute_all_grids = TRUE)."
) |>
  knitr::kable(caption = "ensemble[[model]] slot reference.")
```

## Common navigation patterns {#output-nav}

```{r output-nav}
# 1. Quick convergence summary across all models (curve_id 1)
lapply(ensemble, function(m) {
  fs <- m$fit_stats
  tibble::tibble(
    n_divergent    = fs$n_divergent,
    n_max_treedepth = fs$n_max_treedepth,
    mean_ebfmi     = round(mean(fs$ebfmi, na.rm = TRUE), 3)
  )
}) |>
  dplyr::bind_rows(.id = "model") |>
  knitr::kable(digits = 3, caption = "Quick convergence summary — curve_id 1.")

# 2. Population inflection point: posterior mean and 95% CI
mu_c_draws <- as.numeric(draws_4pl[["mu_c"]])
cat(sprintf(
  "mu_c:  mean = %.3f  95%% CI [%.3f, %.3f]  (log10 AU/mL)\n",
  mean(mu_c_draws),
  quantile(mu_c_draws, 0.025),
  quantile(mu_c_draws, 0.975)
))

# 3. Formal LOO comparison (if more than one model was fitted)
if (!is.null(loo_comparison)) print(loo_comparison)

# 4. Access CDAN grid for the best model at curve_id 1
grid_best <- cr1$grid
head(grid_best[, c("x_fit", "predicted_response",
                   "pcov", "pcov_rmse", "pcov_pass")])

# 5. Access per-model grid for logistic4 specifically
grid_4pl <- ensemble[["logistic4"]]$grid
head(grid_4pl[, c("x_fit", "predicted_response", "pcov")])
```

---

# The hierarchical Stan model {#model}

## Why hierarchical? {#why-hier}

A pooled model treats all plates as a single experiment, conflating
within-plate and between-plate variance and producing overconfident
predictions.
A separate-plate model fits each plate independently, discarding the
shared biology and producing underconfident estimates when any single
plate has few calibrators.
The Bayesian hierarchical model occupies the optimal middle ground:
plate-level parameters are exchangeable draws from a common population
distribution, sharing information across plates while still adapting
to each plate's data.

## Parameter structure {#param-structure}

All model families share the same hierarchical skeleton.
Using the 4PL logistic (`logistic4`) as the reference:

$$
y_{i,k} \;=\; A_k + \frac{D_k - A_k}{1 + \left(\dfrac{x_i}{C_k}\right)^{B_k}}
\;+\; \varepsilon_{i,k}
$$

where $k$ indexes `curve_id`, $x_i$ is the log10-concentration of
standard $i$ (the `concentration` column after preprocessing), and
$\varepsilon_{i,k}$ is observation noise.

| Parameter | Meaning | Hierarchy level |
|-----------|---------|-----------------|
| $A_k$ | Lower asymptote (background) | Per-`curve_id` |
| $B_k$ | Hill slope | Per-`curve_id` |
| $C_k$ | Inflection point (log10-EC50) | Per-`curve_id` |
| $D_k$ | Upper asymptote | Per-`curve_id` |
| $\mu_A, \sigma_A$ … | Population mean and SD for each parameter | Global |
| $\sigma_\varepsilon, \nu$ | Observation noise SD and Student-t d.f. | Global (pooled) |

`logistic5` and `loglogistic5` add a per-`curve_id` asymmetry
parameter $G_k$ with its own population mean and SD.
`gompertz4` replaces the logistic link with a Gompertz function but
keeps the same four-parameter hierarchy.

On the log–log scale (`is_log_independent = TRUE`, `is_log_response = TRUE`),
`loglogistic4` is mathematically equivalent to `logistic4`.
`fit_calibration_bayes()` therefore automatically drops `loglogistic4`
from the candidate set when both transformations are active.

## The Stan models shipped with curveRbayes {#stan-files}

Five Stan model files live in `inst/stan/`.
Each implements the same three-part structure:

| File | Family | Notes |
|---|---|---|
| `hierarchical_logistic4.stan` | 4PL logistic | Reference model |
| `hierarchical_logistic5.stan` | 5PL logistic | Adds asymmetry parameter $G_k$ |
| `hierarchical_loglogistic4.stan` | 4PL log-logistic | Dropped automatically when both axes are log-transformed |
| `hierarchical_loglogistic5.stan` | 5PL log-logistic | |
| `hierarchical_gompertz4.stan` | Gompertz | Replaces logistic link |

Paths are resolved by `stan_model_path()` and models are compiled
(and cached) once per session by `compile_stan_model()`.

## Non-centred parameterisation {#ncp}

The centred parameterisation $\theta_k \sim \mathcal{N}(\mu, \sigma)$
creates a *funnel geometry*: when $\sigma$ is small the sampler must
simultaneously explore a tight neck and wide wings, producing divergent
transitions.
curveRbayes uses the **non-centred parameterisation (NCP)** throughout:

$$
\theta_k \;=\; \mu_\theta + \sigma_\theta \cdot z_k,
\qquad z_k \sim \mathcal{N}(0, 1)
$$

The sampler explores the standardised offset $z_k$ — which always has
flat $\mathcal{N}(0,1)$ geometry — and the global hyperparameters
$(\mu_\theta, \sigma_\theta)$ independently.
Only at the likelihood evaluation are they recombined into $\theta_k$.
This transformation eliminates the funnel and is the primary reason
Stan achieves near-zero divergences on these models.

The `parameters` and `transformed parameters` blocks for `logistic4`
illustrate the pattern:

```stan
parameters {
  // population hyperparameters (on log scale for positive quantities)
  real mu_log_b;
  real mu_c;          // inflection on the fitting scale
  real mu_log_d;
  real mu_a;          // lower asymptote (fitting scale)

  // population SDs — Half-Normal keeps these positive
  real<lower=0> sigma_a;
  real<lower=0> sigma_log_b;
  real<lower=0> sigma_c;
  real<lower=0> sigma_log_d;

  // non-centred offsets: one per curve_id
  vector[N_plates] z_a;
  vector[N_plates] z_b;
  vector[N_plates] z_c;
  vector[N_plates] z_d;

  // observation noise (pooled across all curve_ids)
  real<lower=0> sigma_obs;
  real<lower=1> nu;
}

transformed parameters {
  // plate-level parameters reconstructed from NCP offsets
  vector[N_plates] a     = mu_a      + sigma_a      * z_a;
  vector[N_plates] b     = exp(mu_log_b + sigma_log_b * z_b);
  vector[N_plates] c_par = mu_c      + sigma_c      * z_c;
  vector[N_plates] d     = exp(mu_log_d + sigma_log_d * z_d);
}
```

Note that `b` and `d` are exponentiated so they remain strictly positive.
The inflection point `c_par` and lower asymptote `a` are left on the
fitting scale (already log10 after preprocessing).

## The `reduce_sum` likelihood {#reduce-sum}

The likelihood loop is parallelised via Stan's `reduce_sum` map-reduce
construct, controlled by the `grainsize` argument of `build_stan_data()`
(default `1L`, which lets Stan choose the grain automatically).
With CmdStan's threading backend this provides near-linear speedup with
the number of CPU cores for large datasets.

---

# Data-adaptive priors and `fixed_a` {#priors}

## Data-adaptive prior construction {#adaptive-priors}

When `fixed_a = NULL` (the default), curveRbayes constructs
weakly-informative priors anchored to the observed data range via
`compute_dynamic_priors()`.
`build_stan_data()` assembles these as named scalar fields in the Stan
data list — `prior_a_mu`, `prior_a_sigma`, `prior_d_mu`, `prior_d_sigma`,
`prior_log_b_mu`, `prior_log_b_sigma`, and either
`prior_c_mu` / `prior_c_sigma` (all families except `loglogistic4`) or
`prior_log_c_mu` / `prior_log_c_sigma` (for `loglogistic4`).
Five-parameter families additionally receive `prior_log_g_sd` and
`prior_log_g_plate_sd`.

```{r prior-table, echo=FALSE}
tibble::tribble(
  ~Parameter,           ~`Population mean prior`,              ~Rationale,
  "a (lower asymptote)","Normal(y_min, 0.3 × y_range)",        "Centred on observed minimum; broadly permissive.",
  "log(b) (Hill slope)","Normal(0, 0.7)",                      "Prior median slope = 1.0; log-scale keeps b > 0.",
  "c (inflection)",     "Normal(x_mid, 0.5 × x_range)",        "Centred on geometric midpoint of concentration range.",
  "log(d) (upper asy.)","Normal(y_max + 0.1 × y_range, 0.3 × y_range)", "Slightly above observed maximum.",
  "sigma_obs",          "Half-Normal(0, 0.1 × y_range)",       "Noise scaled to signal range.",
  "log(g) (asymmetry)", "Normal(0, 0.5) / Normal(0, 0.3)",     "5-parameter only. g = 1 recovers the 4PL; regularised toward symmetry."
) |>
  knitr::kable(
    caption = "Data-adaptive prior structure for logistic4 / gompertz4. y_min, y_max, y_range, x_mid, and x_range are computed from the preprocessed standards."
  )
```

You can inspect the actual prior values that were passed to Stan:

```{r show-priors}
# compute_dynamic_priors() is called internally; call it directly to inspect
priors <- compute_dynamic_priors(
  data              = standards_preprocessed,
  response_variable = bead_assay_example$response_var,
  model_family      = "logistic4"
)
str(priors)
```

## The `fixed_a` soft constraint {#fixed-a}

The lower asymptote $A$ (background signal) can be poorly identified
when the lowest calibrator is not far above background, or when
background varies substantially across plates.
In those situations the posterior of $A$ spreads into implausibly low
territory, pulling the other parameters through their posterior
correlations.

`fixed_a` places an **informative Normal prior** on the population
mean of $A$ (on the fitting scale):

$$
\mu_A \;\sim\; \mathcal{N}\!\left(\texttt{fixed\_a},\;
  \max(|\text{y\_range}| \times 0.01,\; 10^{-4})\right)
$$

The SD is deliberately narrow — roughly 1% of the signal range — to
prevent extreme exploration while still permitting genuine
plate-to-plate variation.
This is a *soft* constraint: strongly informative data can still move
$\mu_A$ away from `fixed_a`.

```{r fixed-a-example, eval=FALSE}
# blank wells for antigen alpha have MFI ≈ 18 (on the raw scale);
# after log10-transform, fixed_a should be log10(18) ≈ 1.255.
fit_fixed_a <- fit_calibration_bayes(
  standards          = standards_preprocessed,
  response_var       = bead_assay_example$response_var,
  model_names        = "logistic4",
  is_log_response    = TRUE,
  is_log_independent = TRUE,
  std_curve_conc     = antigen_settings$standard_curve_concentration,
  fixed_a            = log10(18),
  chains             = 4L,
  warmup             = 1000L,
  sampling           = 1000L,
  seed               = 42
)
```

**When to use `fixed_a`:**

- Fewer than ~6 calibrators and the lowest point is close to background.
- Strong prior knowledge of background from blank wells or historical runs.
- Posterior of $A$ is multimodal or has very wide credible intervals.

**When to leave it `NULL`:**

- The assay spans ≥ 3 log-decades with a clear low-end plateau.
- Background is highly variable and you want the model to learn it.

---

# MCMC diagnostics {#diagnostics}

Bayesian inference is only as trustworthy as the quality of the MCMC
approximation.
curveRbayes surfaces three NUTS-specific diagnostic classes that together
constitute a minimum due-diligence checklist.
All three are stored in `ensemble[[model]]$fit_stats`.

## Accessing diagnostics {#diag-access}

```{r diag-convergence}
# Per-model convergence diagnostics from fit_stats
lapply(ensemble, function(m) {
  fs <- m$fit_stats
  tibble::tibble(
    n_divergent     = fs$n_divergent,
    n_max_treedepth = fs$n_max_treedepth,
    mean_ebfmi      = round(mean(fs$ebfmi, na.rm = TRUE), 3)
  )
}) |>
  dplyr::bind_rows(.id = "model") |>
  knitr::kable(digits = 3, caption = "Convergence flag summary — curve_id 1.")
```

```{r posterior-summary}
# Population-level Rhat and ESS for logistic4
posterior::summarise_draws(
  draws_4pl,
  mean, sd,
  ~posterior::quantile2(.x, probs = c(0.025, 0.975)),
  posterior::default_convergence_measures()
) |>
  dplyr::filter(grepl("^mu_|^sigma_obs|^nu$", variable)) |>
  knitr::kable(digits = 3,
               caption = "Population-level parameter summary — logistic4. Rhat < 1.01 and ess_bulk > 400 indicate adequate convergence.")
```

## Divergent transitions {#divergences}

A divergent transition occurs when the leapfrog integrator takes a
discrete step that departs exponentially from the true Hamiltonian.
Divergences cluster in high-curvature regions of the posterior —
most often the neck of a funnel — and indicate that some part of the
geometry is not being explored correctly.

| Divergence count | Interpretation and action |
|---|---|
| 0 | ✅ Proceed. |
| 1–10 | ⚠️ Increase `adapt_delta` (e.g. 0.97 → 0.99). Inspect pairs plots. |
| > 10 | 🚫 Do not use posterior. Likely model or prior misspecification. |

```{r divergences}
lapply(ensemble, function(m) {
  data.frame(n_divergences = m$fit_stats$n_divergent %||% NA_integer_)
}) |>
  dplyr::bind_rows(.id = "model") |>
  knitr::kable(caption = "Divergent transitions per model.")
```

```{r pairs-plot,
    fig.cap="Pairs plot for logistic4 population parameters. Divergent transitions are highlighted in red. Absence of red points in funnel-shaped regions confirms the non-centred parameterisation is working correctly."}
bayesplot::mcmc_pairs(
  posterior::as_draws_array(cmdstan_fit_4pl$draws()),
  pars          = c("mu_a", "mu_c", "mu_log_d", "sigma_c"),
  off_diag_args = list(size = 0.3, alpha = 0.3),
  np            = bayesplot::nuts_params(cmdstan_fit_4pl)
)
```

## E-BFMI {#ebfmi}

The Energy Bayesian Fraction of Missing Information (E-BFMI) measures
how efficiently the sampler traverses the energy distribution.
Values below **0.2** indicate the sampler is trapped in a local region
and cannot explore the full posterior geometry.

$$
\widehat{\text{E-BFMI}} = \frac{\displaystyle\sum_{n=2}^{N}(H_n - H_{n-1})^2}{\operatorname{Var}(H)}
$$

```{r ebfmi}
lapply(ensemble, function(m) {
  ebfmi <- m$fit_stats$ebfmi
  if (is.null(ebfmi)) return(data.frame(mean_ebfmi = NA_real_))
  data.frame(mean_ebfmi = round(mean(ebfmi, na.rm = TRUE), 3))
}) |>
  dplyr::bind_rows(.id = "model") |>
  dplyr::mutate(flag = ifelse(mean_ebfmi < 0.2, "\u26a0\ufe0f LOW", "\u2705 OK")) |>
  knitr::kable(caption = "Mean E-BFMI per model. Values below 0.2 indicate poor energy exploration.")
```

## Maximum treedepth {#treedepth}

NUTS builds a binary tree, doubling the path length at each level up
to `max_treedepth` (default 12, i.e. $2^{12} = 4096$ leapfrog steps).
When a large fraction of transitions hit the cap, the sampler is being
truncated before it can turn: this does not bias the posterior but
reduces effective samples per second.

```{r treedepth}
lapply(ensemble, function(m) {
  n_max <- m$fit_stats$n_max_treedepth
  if (is.null(n_max)) return(data.frame(n_max_treedepth = NA_integer_))
  data.frame(n_max_treedepth = n_max)
}) |>
  dplyr::bind_rows(.id = "model") |>
  knitr::kable(caption = "Transitions hitting max_treedepth per model.")
```

```{r treedepth-plot,
    fig.cap="Treedepth distribution across all chains for logistic4. Most transitions complete well below the cap, indicating efficient trajectory exploration."}
bayesplot::mcmc_nuts_treedepth(
  bayesplot::nuts_params(cmdstan_fit_4pl),
  lp = bayesplot::log_posterior(cmdstan_fit_4pl)
)
```

---

# LOO-CV model selection and stacking {#loo}

## Leave-one-out cross-validation {#loo-cv}

After fitting, `fit_calibration_bayes()` computes **Pareto-smoothed
importance-sampling LOO-CV** (PSIS-LOO) for every fitted model via the
`loo` package [@vehtari2017].
LOO-CV estimates the expected log predictive density (ELPD) for a
held-out observation without refitting:

$$
\widehat{\text{elpd}}_\text{loo} \;=\;
\sum_{i=1}^{N} \log p(y_i \mid y_{-i})
$$

The **Pareto-$k$** diagnostic flags observations whose importance
weights are unreliable:

| $k$ | Label | Action |
|-----|-------|--------|
| $< 0.5$ | Good | Reliable. |
| $0.5$–$0.7$ | OK | Slightly influential; results usable. |
| $0.7$–$1$ | Bad | Consider moment-matching correction. |
| $\ge 1$ | Very bad | LOO unreliable for this model. |

```{r loo-compare}
if (!is.null(loo_comparison)) loo_comparison
```

```{r pareto-k,
    fig.cap="Pareto-k diagnostic for logistic4. Points above k = 0.7 (dashed line) flag high-leverage calibrators that disproportionately influence the fit."}
if (!is.null(loo_list[["logistic4"]])) {
  plot(loo_list[["logistic4"]],
       diagnostic   = "k",
       label_points = TRUE,
       main         = "Pareto-k — logistic4")
  abline(h = 0.7, lty = 2, col = "firebrick")
}
```

## Bayesian stacking weights {#stacking}

Rather than selecting a single best model, curveRbayes computes
**Bayesian stacking weights** [@yao2018] — the weight vector $\mathbf{w}$
that maximises the stacked ELPD:

$$
\hat{\mathbf{w}} \;=\;
\arg\max_{\mathbf{w}} \sum_{i=1}^{N}
\log \sum_{k=1}^{K} w_k \, p(y_i \mid y_{-i}, \mathcal{M}_k),
\quad w_k \ge 0,\; \textstyle\sum_k w_k = 1
$$

Stacking is preferable to winner-takes-all model selection because it
is **calibrated under model misspecification**: even if no single
candidate is the true data-generating process, the stacked ensemble
achieves the best achievable predictive accuracy from the candidate set.

```{r stacking-weights}
if (!is.null(stacking_weights)) {
  tibble::enframe(stacking_weights, name = "model", value = "weight") |>
    dplyr::arrange(dplyr::desc(weight)) |>
    knitr::kable(digits = 4,
                 caption = "Bayesian stacking weights across candidate models.")
}
```

```{r stacking-bar,
    fig.cap="Stacking weights. A single dominant weight (> 0.9) supports using that model alone; mixed weights suggest genuine model uncertainty."}
if (!is.null(stacking_weights)) {
  tibble::enframe(stacking_weights, name = "model", value = "weight") |>
    ggplot(aes(x = reorder(model, -weight), y = weight, fill = model)) +
    geom_col(width = 0.6, show.legend = FALSE) +
    scale_y_continuous(limits = c(0, 1),
                       labels = scales::percent_format(accuracy = 1)) +
    labs(x = "Model", y = "Stacking weight",
         title = "Bayesian stacking weights") +
    theme_minimal(base_size = 12)
}
```

---

# Eligibility gating {#eligibility}

Before any model's posterior predictions are used for back-calculation,
curveRbayes subjects each `curve_id` × model combination to
**eligibility gates**.
A model that fails a gate is excluded from the ensemble even if its
MCMC diagnostics are clean.
Only two gates are active on the Bayesian path — `at_bound` and
`vcov_condition` are not applicable because priors are soft and there
is no vcov matrix.

## The `rel_se` gate {#rel-se}

For each per-`curve_id` parameter $\theta_k$:

$$
\text{rel\_se}(\theta_k)
= \frac{\operatorname{posterior SD}(\theta_k)}{|\operatorname{posterior mean}(\theta_k)|}
$$

If any parameter's relative SE exceeds `max_rel_se` (default 5.0) the
`curve_id` × model combination is flagged ineligible.
This catches near-unidentified parameters where the likelihood is
essentially flat in one direction — formally valid MCMC but
meaningless predictions.

## The `dynamic_range` gate {#dynamic-range}

The dynamic range is assessed from the CDAN grid's `pcov` profile
— specifically, the log10-distance between the LLOQ and ULOQ
(the concentration range where `pcov < pcov_threshold`).
A model whose quantifiable range spans less than `min_dynamic_range_log10`
decades (default 0.5) is flagged ineligible.

A model is **globally eligible** only if it passes both gates on
**all** `curve_id` values.

```{r eligibility}
if (!is.null(eligibility) && nrow(eligibility) > 0) {
  eligibility |>
    dplyr::select(model, curve_id, dplyr::any_of(c("gate", "passed", "detail")),
                  eligible) |>
    dplyr::arrange(model, curve_id) |>
    knitr::kable(digits = 3,
                 caption = "Eligibility gate results. eligible = FALSE excludes that model × curve_id from back-calculation.")
}
```

```{r eligibility-summary}
if (!is.null(eligibility) && nrow(eligibility) > 0 &&
    "eligible" %in% names(eligibility)) {
  eligibility |>
    dplyr::group_by(model) |>
    dplyr::summarise(
      n_curve_ids = dplyr::n_distinct(curve_id),
      n_failures  = sum(!eligible),
      all_passed  = all(eligible),
      .groups     = "drop"
    ) |>
    knitr::kable(caption = "Eligibility summary across all models.")
}
```

---

# CDAN precision grids {#cdan-grids}

## What is a CDAN precision grid? {#cdan-concept}

**CDAN** (Concentration-Dependent Assay Noise) precision profiling
[@omalley_theory_2003; @omalley_bayesian_2008] characterises *how
accurately* a calibration curve can back-calculate an unknown
concentration as a function of where that concentration falls on the
curve.
Near the inflection point the curve is steep — small response uncertainty
maps to small concentration uncertainty.
Near the asymptotes the curve is flat — the same response uncertainty
maps to large concentration uncertainty.

The CDAN grid makes this relationship explicit: a dense grid of
concentration values, each with its posterior predictive back-calculation
distribution and associated %CV, incorporating both curve-parameter
uncertainty *and* the additional measurement noise that a real instrument
observation would contribute.

## Grid columns {#grid-columns}

```{r grid-col-table, echo=FALSE}
tibble::tribble(
  ~Column,                    ~Description,
  "x_fit",                    "Grid concentration on the fitting scale (log10 AU/mL when is_log_independent = TRUE).",
  "predicted_response",       "Posterior mean of the forward-predicted response (mean of y_mat across draws).",
  "ci_lower / ci_upper",      "2.5th and 97.5th percentiles of forward-predicted response across draws.",
  "predicted_concentration",  "Posterior median of back-calculated concentration across CDAN draws.",
  "se_concentration",         "Posterior SD of back-calculated concentration.",
  "pcov",                     "% CV of back-calculated concentration. For log-scale x: se_concentration × log(10) × 100, capped at cv_x_max.",
  "pcov_rmse",                "Relative RMSE of back-calculated concentration versus the true grid point (CDAN precision, O'Malley 2008).",
  "pcov_pass",                "Logical: pcov < pcov_threshold.",
  "d2y_dx2",                  "Second derivative of the response curve — used by curveRcore::compute_shape_loq_from_grid() to locate shape-based LLOQ/ULOQ."
) |>
  knitr::kable(caption = "Columns in the CDAN grid data frame.")
```

## Accessing and plotting grids {#grid-access}

```{r grid-structure}
dplyr::glimpse(cr1$grid)
```

```{r grid-plot,
    fig.cap="Per-model CDAN precision profiles: back-calculation %CV versus log10(concentration) for all curve_ids. The dashed line marks 20% CV — a typical regulatory acceptability threshold. The ribbon spans the range across curve_ids; the line is the mean."}
all_grids <- purrr::map_dfr(
  names(ensemble),
  function(m) {
    g <- ensemble[[m]]$grid
    if (is.null(g)) return(NULL)
    dplyr::mutate(g, model = m)
  }
)

if (nrow(all_grids) > 0 && "x_fit" %in% names(all_grids)) {
  all_grids |>
    dplyr::group_by(model, x_fit) |>
    dplyr::summarise(
      cv_mean = mean(pcov,  na.rm = TRUE),
      cv_lo   = min(pcov,   na.rm = TRUE),
      cv_hi   = max(pcov,   na.rm = TRUE),
      .groups = "drop"
    ) |>
    ggplot(aes(x = x_fit, colour = model, fill = model)) +
    geom_ribbon(aes(ymin = cv_lo, ymax = cv_hi),
                alpha = 0.15, colour = NA) +
    geom_line(aes(y = cv_mean), linewidth = 0.8) +
    geom_hline(yintercept = 20, linetype = "dashed",
               colour = "grey40", linewidth = 0.6) +
    scale_x_continuous(
      name   = "log\u2081\u2080(concentration)  [AU/mL]",
      breaks = seq(-3, 2, by = 1)
    ) +
    scale_y_continuous(name = "Back-calculation CV (%)", limits = c(0, NA)) +
    facet_wrap(~model, nrow = 2) +
    theme_minimal(base_size = 11) +
    theme(legend.position = "none") +
    labs(title    = "CDAN precision profiles — all models",
         subtitle = "Ribbon = range across curve_ids; line = mean")
}
```

---

# The CDAN three-step noise injection procedure {#cdan-procedure}

`predict_grid_bayes()` constructs the CDAN precision profile at each
grid concentration $x^*$ via a three-step procedure that propagates
both curve-parameter uncertainty and instrument measurement noise.

## Step 1 — draw posterior curve parameters {#step1}

For each of the $S$ posterior samples, retrieve the full set of
per-`curve_id` parameters:

$$
\boldsymbol{\theta}_k^{(s)}
= \left\{A_k^{(s)},\; B_k^{(s)},\; C_k^{(s)},\; D_k^{(s)}\right\}
$$

This captures **parameter uncertainty**: how much the curve shape
varies across the posterior.

## Step 2 — evaluate the forward model {#step2}

For each sample $s$ and `curve_id` $k$, evaluate the forward model
at $x^*$ (log10-concentration):

$$
\tilde{y}^{(s,k)}
= A_k^{(s)}
+ \frac{D_k^{(s)} - A_k^{(s)}}
       {1 + \left(x^* / C_k^{(s)}\right)^{B_k^{(s)}}}
$$

(For `gompertz4` the Gompertz link replaces the logistic fraction;
for `logistic5`/`loglogistic5` the asymmetry parameter $G_k^{(s)}$
modifies the denominator.)

## Step 3 — inject Student-t noise and invert {#step3}

**This step is unique to `predict_grid_bayes()` and defines CDAN.**

To each forward-predicted response $\tilde{y}^{(s,k)}$, add a noise
draw from the posterior predictive distribution:

$$
y^{*(s,k)}
= \tilde{y}^{(s,k)}
  + \varepsilon^{(s)},
\qquad
\varepsilon^{(s)} \sim t_{\nu^{(s)}}\!\left(0,\; \sigma_\varepsilon^{(s)}\right)
$$

where $\sigma_\varepsilon^{(s)}$ and $\nu^{(s)}$ are themselves
drawn from the posterior — both `sigma_obs` and `nu` are estimated
parameters in the Stan model.
The heavy tails of the Student-t distribution provide a realistic
characterisation of occasional outlier instrument readings.

The noisy response $y^{*(s,k)}$ is then **back-calculated** through
the analytical inverse of the forward model:

$$
\hat{x}^{(s,k)}
= f^{-1}\!\left(y^{*(s,k)};\; \boldsymbol{\theta}_k^{(s)}\right)
$$

The collection $\left\{\hat{x}^{(s,k)}\right\}$ is the CDAN
back-calculation distribution at $x^*$.
The `pcov` column is the SD of this collection, divided by the
mean, expressed as a percentage (computed on the fitting scale and
converted to the linear CV via $\text{pcov} = \text{SE} \times \ln(10) \times 100$).
The `pcov_rmse` column is the relative RMSE against the known true
grid point — the O'Malley (2008) CDAN precision metric.

The entire three-step logic can be illustrated concisely:

```{r cdan-demo}
set.seed(123)

# Extract 400 posterior samples for logistic4
draws_mat <- posterior::as_draws_matrix(cmdstan_fit_4pl$draws())
idx       <- sample(nrow(draws_mat), 400)
samp      <- draws_mat[idx, ]

# Plate-level parameters for curve_id = 1
A         <- as.numeric(samp[, "a[1]"])
B         <- as.numeric(samp[, "b[1]"])
C         <- as.numeric(samp[, "c_par[1]"])
D         <- as.numeric(samp[, "d[1]"])
sigma_obs <- as.numeric(samp[, "sigma_obs"])
nu        <- as.numeric(samp[, "nu"])

# Grid point: log10(1 AU/mL) = 0
x_star <- 0

# Step 1–2: forward prediction using curveRcore::logistic4()
y_tilde <- curveRcore::logistic4(x_star, A, B, C, D)

# Step 3: inject Student-t noise (posterior nu), then invert
eps    <- rt(length(y_tilde), df = median(nu)) * sigma_obs
y_star <- y_tilde + eps

# Back-calculate using curveRcore analytical inverse
x_hat <- vapply(seq_along(A), function(s) {
  tryCatch(
    curveRcore::inv_logistic4(y_star[s], A[s], B[s], C[s], D[s]),
    error = function(e) NA_real_
  )
}, numeric(1))
x_hat <- x_hat[is.finite(x_hat)]

cat(sprintf(
  "CDAN back-calculation at log10(x*) = %.1f  [x* = %.0f AU/mL]\n",
  x_star, 10^x_star
))
cat(sprintf("  Posterior mean:  %.4f  log10(AU/mL)\n", mean(x_hat, na.rm = TRUE)))
cat(sprintf("  Posterior SD:    %.4f  log10(AU/mL)\n",   sd(x_hat, na.rm = TRUE)))
cat(sprintf("  Back-calc CV:    %.1f%%\n",
            sd(x_hat, na.rm = TRUE) * log(10) * 100))
```

---

# Back-calculating test samples {#backcalc}

## Why noise is NOT injected for test samples {#no-noise}

This is the most important conceptual distinction in the package.

When `predict_samples_bayes()` is called on observed test-sample
responses, the situation is fundamentally different from building
a CDAN grid:

> **The observed response $y_\text{obs}$ already IS the noisy
> measurement. Injecting noise again would be double-counting.**

The back-calculation task is: *given that the instrument returned
$y_\text{obs}$, what is the posterior distribution of the unknown
concentration $x$?*
This is a pure inversion problem:

$$
\hat{x}^{(s)}
= f^{-1}\!\left(y_\text{obs};\; \boldsymbol{\theta}_k^{(s)}\right)
$$

No noise draw appears.
The uncertainty in $\hat{x}^{(s)}$ arises solely from posterior
uncertainty in the curve parameters $\boldsymbol{\theta}_k^{(s)}$.

| Scenario | Function | Noise injected? | Source of uncertainty |
|---|---|---|---|
| CDAN precision grid | `predict_grid_bayes()` | ✅ Yes — Student-t($\nu$, $\sigma_\text{obs}$) from posterior | Parameter uncertainty **+** hypothetical measurement noise |
| Test sample back-calculation | `predict_samples_bayes()` | ❌ No | Parameter uncertainty only (noise already realised in $y_\text{obs}$) |

## Running back-calculation {#backcalc-run}

Test samples need only `curve_id` and the response column (`mfi`).
No `concentration` column is needed or expected — that is what is
being estimated.
Back-calculation is run automatically inside `fit_calibration_bayes()`
whenever `samples` is provided; use `collect_samples_bayes()` to
extract the full table.

```{r backcalc}
# Collect all sample back-calculations across all curve_ids
results <- collect_samples_bayes(fit)

if (!is.null(results) && nrow(results) > 0) {
  results[1:min(6, nrow(results)),
          c("curve_id", "sampleid", "mfi",
            "predicted_concentration", "final_concentration",
            "se_concentration", "pcov", "pcov_pass")] |>
    knitr::kable(digits = 3,
                 caption = "Back-calculated concentrations (first rows). predicted_concentration is on the log10(AU/mL) fitting scale; final_concentration is on the natural scale after dilution correction.")
} else {
  cat("No sample predictions available.\n")
}
```

```{r backcalc-plot,
    fig.cap="Back-calculated concentrations for all samples (log10 scale). Colour indicates whether the sample falls within the quantifiable range (pcov_pass)."}
if (!is.null(results) && nrow(results) > 0 &&
    "predicted_concentration" %in% names(results)) {
  ggplot(results,
         aes(x = factor(curve_id),
             y = predicted_concentration,
             colour = pcov_pass)) +
    geom_jitter(width = 0.2, size = 1.5, alpha = 0.7) +
    labs(
      x      = "curve_id",
      y      = "Predicted concentration (log10 AU/mL)",
      colour = "pcov_pass",
      title  = "Back-calculated concentrations"
    ) +
    theme_minimal(base_size = 12) +
    theme(legend.position = "bottom")
}
```

---

# Extracting summaries {#summaries}

`summary_table_bayes()` returns one row per `curve_id` with the best
model name, per-parameter posterior mean and SD, and NUTS diagnostics.
`collect_samples_bayes()` returns a flat data frame of all
back-calculated test samples with `curve_id` prepended.

```{r summaries}
# One-row-per-curve summary
summary_table_bayes(fit) |>
  knitr::kable(digits = 3,
               caption = "Per-curve summary: best model, posterior means and SDs, NUTS diagnostics.")
```

Both functions also accept the legacy single-`calibration_result` format
(i.e. a single plate object), so they work identically on
`fit$plates[["1"]]` and on the full multiplate object.

---

# References

<div id="refs"></div>

---

# Session information {#session}

```{r session}
sessionInfo()
```
